Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-02-02 cordillera-cycle.tex
One last small correction.

      Ice sheet dynamics are typically modelled using a~combination of
      internal deformation and basal sliding. PISM is a~shallow ice sheet
      model, which implies that the balance of stresses is approximated
      based on their predominant components. The Shallow Shelf Approximation
      (SSA) is combined with the Shallow Ice Approximation
      (SIA) by adding velocity solutions of the two approximations
      \citep[Eqs.~7--9 and 15]{Winkelmann.etal.2011}. Although this
      heuristic imply errors in the transition zone where gravitational
      stresses intervene both in the SIA and SSA velocity computation, this
      hybrid scheme is computationally much more efficient than a fully
      three-dimensional model with which the simulations presented here
      would not be feasible.

>>>>

      Ice sheet dynamics are typically modelled using a~combination of
      internal deformation and basal sliding. PISM is a~shallow ice sheet
      model, which implies that the balance of stresses is approximated
      based on their predominant components. The Shallow Shelf Approximation
      (SSA) is combined with the Shallow Ice Approximation
      (SIA) by adding velocity solutions of the two approximations
      \citep[Eqs.~7--9 and 15]{Winkelmann.etal.2011}. Although this
      heuristic approach implies errors in the transition zone where gravitational
      stresses intervene both in the SIA and SSA velocity computation, this
      hybrid scheme is computationally much more efficient than a fully
      three-dimensional model with which the simulations presented here
      would not be feasible.
